### 2018-09-02 paper/preliminaries.tex
small problem with nondeterminism

Failures refinement, $P \lessdet_F Q$, is defined as expected by set
containment $\fails(Q)\subseteq\fails(P)$. Since refusals are subset-closed,
$(s,\varnothing)\in\fails(P)$ for all traces $s\in\trc(Q)$. So, for
divergences-free processes, failures refinement implies trace refinement.
Therefore, using the conformance relation $conf$ 
\begin{equation}\label{eq:conf}
  Q\ conf\ P \defs \forall s\in \trc(P) \cap \trc(Q): \refs(Q/s)
  \subseteq \refs(P/s),
\end{equation}
failures refinement can be expressed by $\lessdet_T$ and $conf$.
\begin{equation}\label{thm:fref-tref-conf}
(P \lessdet_F Q) \iff (P \lessdet_T Q \land Q\ conf\ P)
\end{equation}
%
Throughout this paper, the alphabet of the processes, that is the set of
events that are in scope, is denoted by $\Sigma$ and supposed to be finite.
%Since we are only
%considering ``classical'' CSP processes, the alphabet is always finite.
The FDR tool~\cite{fdr} supports model checking and semantic analyses of
finite-state CSP processes.

@@

As shown in~\cite{Roscoe:1994:CME:197600}, the failures semantics of any
finite-state CSP process $P$ can be represented by a \emph{normalised
transition graph} $G(P)$ defined by a tuple
$$
G(P) = ( N, \ii n, \Sigma, t : N\times\Sigma \pfun N, r : N \fun \mathbb{P}\mathbb{P}(\Sigma)),
$$
with nodes $N$, initial node $\ii n\in N$, and process alphabet $\Sigma$. The
partial \emph{transition function} $t$ maps a node $n$ and an event
$e\in\Sigma$ to its successor node $t(n,e)$. If $(n,e)$ is in the domain of
$t$, then there is a transition, that is, an outgoing edge, from $n$ with
label $e$, leading to node $t(n,e)$. Normalisation of $G(P)$ is reflected by
the fact that $t$ is a function. The graph construction
in~\cite{Roscoe:1994:CME:197600} implies that all nodes $n$ in $N$ are
reachable by sequences of edges labelled by $e_1\dots e_k$ and connecting
states $\ii n,n_1,\dots,n_{k-1},n$, such that
\[
n_1 = t(\ii n,e_1), \quad n_i = t(n_{i-1},e_i),\ i = 2,\dots,k-1,\quad
n= t(n_{k-1},e_k).
\]
%
By construction, $s\in\Sigma^*$ is a trace of $P$, if, and only if, there is
a path through $G(P)$ starting  at $\ii n$ whose edge labels coincide with
$s$. In analogy to $\trc(P)$, we use notation $\trc(G(P))$ for the set of
finite, initialised paths through $G(P)$, each path represented by its finite
sequence of edge labels, and we note that $\trc(P) = \trc(G(P))$. Since
$G(P)$ is normalised, there is a unique node reached by applying the events
from $s$ one by one, starting in $\ii n$. Therefore, $G(P)/s$  is also well
defined. By $[n]^0$ we denote the \emph{initials} of $n$:~the set of events
occurring as labels in any outgoing transitions.
$$
[n]^0 = \{ e\in\Sigma~|~(n,e)\in\dom~t \}
$$
The graph construction from~\cite{Roscoe:1994:CME:197600} used to define
$G(P)$ for any process $P$ guarantees that $[G(P)/s]^0 = [P/s]^0$ for all
traces $s$ of $P$.

@@

When investigating  tests for failures refinement, the notion of
\emph{acceptances}~\cite{Hennessy:1988:ATP:50497}, which is dual to refusals,
is also useful. An acceptance set of $P/s$ is a subset of its initials
$[P/s]^0$; equivalently, it is a subset of events labelling  outgoing transitions of
$G(P)/s$. If the behaviour of  $P/s$ is deterministic, its only acceptance
equals $[P/s]^0$, because $P/s$ never refuses any of the events contained in
this set. If $P/s$ is nondeterministic, it internally chooses one of its
\emph{minimal acceptance sets} $A$ and never refuses any event in $A$, while
{\it possibly} refusing the events from $[P/s]^0 - A$ and
{\it always} refusing those from $\Sigma - [P/s]^0$.
The acceptances of $P/s$ are denoted by
$\accs(P/s)$, and the minimal acceptances by $\minaccs(P/s)$. They satisfy
the following properties.
%
\begin{eqnarray}
A\in \minaccs(P/s) & \Leftrightarrow & \exists R\in\maxrefs(P/s) \wedge A = \Sigma-R
\label{eq:accref}
\\
\bigcup \{ A~|~A\in \accs(P/s)\} & = & [P/s]^0
\label{eq:accinitials}
\\
 X\in\accs(P/s) &\Leftrightarrow & A\in \minaccs(P/s) \wedge A\subseteq X \subseteq [P/s]^0
 \label{eq:accsubset}
\end{eqnarray}
%
%Note that (\ref{eq:accref}) can be regarded as a definition of minimal
%acceptances by means of maximal refusals. In this case,
%(\ref{eq:accinitials}) and (\ref{eq:accsubset}) are consequences of this
%definition and the fact that refusals are subset-closed. \fixme{alcc: are you
%sure? (4) does not talk about Acc. Is this important?}
%\fixme{jp: I'm sure and I can prove this. However, we don't need this fact, so I suggest to
%removed it.}
%
Exploiting formulas (\ref{eq:accref}), (\ref{eq:accinitials}), and
(\ref{eq:accsubset}), every node of a normalised transition graph can
alternatively be labelled with their minimal acceptances, and this
information is equivalent to that contained in the maximal refusals. Since
process states $P/s$ are equivalently expressed by states $G(P)/s$ of $P$'s
normalised transition graph, we also write $\minaccs(G(P)/s)$ and
note that (\ref{eq:refsAndR}) and (\ref{eq:accref}) imply
\begin{equation}\label{eq:maxrefsminaccs}
\minaccs(G(P)/s) = \{ \Sigma - R | R\in r(G(P)/s) \}.
\end{equation}

@@

\begin{example}\label{ex:a}
We consider the process $P$ in Example~\ref{example:CSP}; its transition
graph $G(P)$ is shown in Fig.~\ref{fig:tga}. The process state
$P/\varepsilon$ (where $\varepsilon$ denotes the empty trace) is represented
as Node\_0, with $\{ a\}$ as the only minimal acceptance, since $a$ is never
refused and no other events are accepted. Having engaged in $a$, the
transition from Node\_0 leads to Node\_2 representing the process state $P/a
= Q\intchoice R$. The internal choice induces several minimal
acceptances derived from $Q$ and $R$. Since these processes accept their
initial events in external choice, $Q\intchoice R$ induces minimal acceptance
sets $\{a,c\}$ and $\{b,c\}$. Note that event $c$ can never be refused, since
it is contained in each minimal acceptance set.

Having engaged into $c$, the next process state is represented by Node\_1.
Due to normalisation, there is only a single transition satisfying
$t(\text{Node\_2},c) = \text{Node\_1}$. This transition, however, can have
been caused by either $Q$ or $R$ engaging into $c$, so Node\_1 corresponds to
process state $Q/c \intchoice R/c = P \intchoice R$. This is reflected by the
two minimal acceptance sets labelling Node\_1.
Similar considerations explain the other nodes and transitions in
Fig.~\ref{fig:tga}.

Note that the node names including their number suffixes are generated by the
FDR tool. The numbering is generated during the normalisation procedure. So,
the node numbers do not reflect the distance from the initial node Node\_0.
\xbox
\end{example}

Summarising, refinement relations between finite-state CSP processes $P, Q$ can be be
expressed by means of their normalised transition graphs
\begin{eqnarray*}
G(P) & = & ( N_P, {\ii n}_P, \Sigma, t_P : N_P\times\Sigma \pfun N_P, r_P : N_P \fun \mathbb{P}\mathbb{P}(\Sigma))
\\
G(Q) & = & ( N_Q, {\ii n}_Q, \Sigma, t_Q : N_Q\times\Sigma \pfun N_Q, r_Q : N_Q \fun \mathbb{P}\mathbb{P}(\Sigma))
\end{eqnarray*}
%
as established by results in the following lemma.
%
\begin{lemma}
  \label{lemma:tgtrcref}
  \begin{eqnarray}
  P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
  \label{eq:trcrefa}
  \\
  \label{eq:failconf}
  P \lessdet_F Q & \Leftrightarrow & P \lessdet_T Q \wedge P\ conf\ Q
  \\
  \label{eq:failrefa}
  P\ conf\ Q & \Leftrightarrow & \nonumber
  \forall s\in\trc(G(Q))\cap \trc(G(P)), R_Q\in r_Q(G(Q)/s):  \nonumber
  \\ & & \tabd
  \exists R_P\in r_P(G(P)/s): R_Q\subseteq R_P
  \\
  \label{eq:failrefb}
   & \Leftrightarrow &
    \forall s\in\trc(G(Q))\cap \trc(G(P)), A_Q\in\minaccs(G(Q)/s):  \nonumber
   \\ & & \tabd
  \exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
 \end{eqnarray}
  \xbox
\end{lemma}
%
The result (\ref{eq:trcrefa}) reflects trace refinement in terms of graph
traces; (\ref{eq:failconf}) expresses failures refinement in terms of traces
refinement and $conf$; (\ref{eq:failrefa}) states how $conf$ can be expressed
by means of the maximal refusal functions of the graphs involved; and
(\ref{eq:failrefb}) states the same in terms of the minimal acceptances that
can be derived from the maximal refusal functions by means of
(\ref{eq:maxrefsminaccs}). \fixme{alcc: I think at least the report should
point to proofs.}

% =========================================================================
\subsubsection*{Reachability Under Sets of Traces}
\label{sec:V} Given a finite-state CSP process $P$ and its normalised
transition graph $G(P)$,
%\[
%G(P) = ( N, \ii n, \Sigma, t : N\times\Sigma \pfun N, r : N \fun \mathbb{P}\mathbb{P}(\Sigma)),
%\]
suppose that $V\subseteq\Sigma^*$ is a prefix-closed set  of sequences of
events. By $t(\ii n,V)$ we denote the set
\[
t(\ii n,V) = \{ n\in N~|~\exists s\in V: s\in\trc(P)\wedge G(P)/s = n \}
\]
of nodes in $N$ that are reachable in $G(P)$ by applying traces of $V$. The
lemma below specifies a construction method for such sets $V$ reaching {\it
every} node of $N$.

@@

For proving our main theorems, it is necessary to consider the \emph{product}
of normalised transition graphs. We need this only for the investigation of
corresponding traces in reference processes and processes for SUTs. So, the
labelling of nodes with maximal refusals or minimal acceptances are
disregarded in the product construction. We consider two normalised
transition graphs
\[
G_i = ( N_i, \ii n_i, \Sigma, t_i : N_i\times\Sigma \pfun N_i, r_i : N_i \fun \mathbb{P}\mathbb{P}(\Sigma)),\qquad i = 1,2,
\]
over the same alphabet $\Sigma$. Their product is defined by
%
\begin{eqnarray}
G_1\times G_2 & = & (N_1\times N_2,(\ii n_1,\ii n_2), t:(N_1\times N_2)\times\Sigma\pfun (N_1\times N_2))
\\
\dom~t & = & \{ ((n_1,n_2),e)\in (N_1\times N_2)\times\Sigma~|   \nonumber
\\ & & \tabc
(n_1,e)\in\dom~t_1\wedge
(n_2,e) \in\dom~t_2    \}
\\
t((n_1,n_2),e) & = & (t_1(n_1,e),t_2(n_2,e))\ \text{for $((n_1,n_2),e)\in\dom~t$}
\end{eqnarray}
%
The following lemma is used in the proof of our main theorem.
%
\begin{lemma}\label{lemma:reachproduc}
If $G_1$ has $p$ states and $G_2$ has $q$ states, then every reachable state
$(n_1,n_2)$ of the product graph $G_1\times G_2$ can be reached by a trace
%%%$s\in\trc(G_1)\cap \trc(G_2)$  we don't need this
of maximal length $(pq-1)$.
\end{lemma}
\begin{proof}
The product graph $G_1\times G_2$ has at most $pq$ states. The empty trace $\varepsilon$
reaches its initial state $(\ii n_1,\ii n_2)$. Applying Lemma~\ref{lemma:extendV}
$(pq-1)$ times with $V=\{\varepsilon \}$ implies that $G_1\times G_2$ reaches
all of its reachable states (there are at most $pq$ of them) under
$V' = V \cup V.\Sigma\cup\dots \cup V.\Sigma^{(pq-1)}$. The maximal length of traces in
$V'$ is $(pq-1)$.
\xbox
\end{proof}

@@

\item For all $s\in\trc(P)\cap \trc(Q)$ and $H \in  \minhits(P/s)$, $H$ is
a (not necessariliy minimal) hitting set of $\minaccs(Q/s)$.
\end{enumerate}
\end{lemma}
\begin{proof}
For showing ``$1 \Rightarrow 2$'', assume   $P\ conf\ Q$ and
  $s\in\trc(P)\cap \trc(Q)$. Lemma~\ref{lemma:tgtrcref},
(\ref{eq:failrefb}), states that
\[
\forall A_Q\in\minaccs(G(Q)/s):
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\]
Therefore, $H \in  \minhits(P/s)$ not only implies $H\cap A_P\neq\varnothing$
for all minimal acceptances $A_P$, but also $H\cap A_Q\neq\varnothing$ for
every minimal acceptance $A_Q$, because $A_P\subseteq A_Q$ for at least one
$A_P$. As a consequence, each $H \in \minhits(P/s)$ is also a hitting set for
$\minaccs(G(Q)/s)$ as required.

>>>>

Failures refinement, $P \lessdet_F Q$, is defined as expected by set
containment $\fails(Q)\subseteq\fails(P)$. Since refusals are subset-closed,
$(s,\varnothing)\in\fails(P)$ for all traces $s\in\trc(Q)$. So, for
divergences-free processes, failures refinement implies trace refinement.
Therefore, using the conformance relation
%
\begin{equation}\label{eq:conf}
  Q\ conf\ P \defs \forall s\in \trc(P) \cap \trc(Q): \refs(Q/s)
  \subseteq \refs(P/s),
\end{equation}
%
failures refinement can be expressed by $\lessdet_T$ and $conf$.
%
\begin{equation}\label{thm:fref-tref-conf}
(P \lessdet_F Q) \iff (P \lessdet_T Q \land Q\ conf\ P)
\end{equation}
%
Throughout this paper, the alphabet of the processes, that is the set of
events that are in scope, is denoted by $\Sigma$ and supposed to be finite.
%Since we are only
%considering ``classical'' CSP processes, the alphabet is always finite.
The FDR tool~\cite{fdr} supports model checking and semantic analyses of
finite-state CSP processes.

@@

As shown in~\cite{Roscoe:1994:CME:197600}, the failures semantics of any
finite-state CSP process $P$ can be represented by a \emph{normalised
transition graph} $G(P)$ defined by a tuple
$$
G(P) = ( N, \ii n, \Sigma, t : N\times\Sigma \pfun N, r : N \fun \mathbb{P}\mathbb{P}(\Sigma)),
$$
with nodes $N$, initial node $\ii n\in N$, and process alphabet $\Sigma$. The
partial \emph{transition function} $t$ maps a node $n$ and an event
$e\in\Sigma$ to its successor node $t(n,e)$. If $(n,e)$ is in the domain of
$t$, then there is a transition, that is, an outgoing edge, from $n$ with
label $e$, leading to node $t(n,e)$. Normalisation of $G(P)$ is reflected by
the fact that $t$ is a function. The graph construction
in~\cite{Roscoe:1994:CME:197600} implies that all nodes $n$ in $N$ are
reachable by sequences of edges labelled by $e_1\dots e_k$ and connecting
states $\ii n,n_1,\dots,n_{k-1},n$, such that
\[
n_1 = t(\ii n,e_1), \quad n_i = t(n_{i-1},e_i),\ i = 2,\dots,k-1,\quad
n= t(n_{k-1},e_k).
\]
%
By construction, $s\in\Sigma^*$ is a trace of $P$, if, and only if, there is
a path through $G(P)$ starting  at $\ii n$ whose edge labels coincide with
$s$. In analogy to $\trc(P)$, we use the notation $\trc(G(P))$ for the set of
finite, initialised paths through $G(P)$, each path represented by its finite
sequence of edge labels. We note that $\trc(P) = \trc(G(P))$. Since $G(P)$ is
normalised, there is a unique node reached by applying the events from $s$
one by one, starting in $\ii n$. Therefore, $G(P)/s$  is also well defined.
By $[n]^0$ we denote the \emph{initials} of $n$:~the set of events occurring
as labels in any outgoing transitions.
$$
[n]^0 = \{ e\in\Sigma~|~(n,e)\in\dom~t \}
$$
The graph construction from~\cite{Roscoe:1994:CME:197600} used to define
$G(P)$ for any process $P$ guarantees that $[G(P)/s]^0 = [P/s]^0$ for all
traces $s$ of $P$.

@@

When investigating  tests for failures refinement, the notion of
\emph{acceptances}~\cite{Hennessy:1988:ATP:50497}, which is dual to refusals,
is also useful. An acceptance set of $P/s$ is a subset of its initials
$[P/s]^0$; equivalently, it is a subset of events labelling  outgoing transitions of
$G(P)/s$. If the behaviour of  $P/s$ is deterministic, its only acceptance
equals $[P/s]^0$, because $P/s$ never refuses any of the events contained in
this set. If $P/s$ is nondeterministic, it internally chooses one of its
\emph{minimal acceptance sets} $A$ and never refuses any event in $A$, while
{\it possibly} refusing the events from $[P/s]^0 - A$ and
{\it always} refusing those from $\Sigma - [P/s]^0$.
The acceptances of $P/s$ are denoted by
$\accs(P/s)$, and the minimal acceptances by $\minaccs(P/s)$. They satisfy
the following properties.
%
\begin{eqnarray}
A\in \minaccs(P/s) & \Leftrightarrow & \exists R\in\maxrefs(P/s) \wedge A = \Sigma-R
\label{eq:accref}
\\
\bigcup \{ A~|~A\in \accs(P/s)\} & = & [P/s]^0
\label{eq:accinitials}
\\
 X\in\accs(P/s) &\Leftrightarrow & A\in \minaccs(P/s) \wedge A\subseteq X \subseteq [P/s]^0
 \label{eq:accsubset}
\end{eqnarray}
%
%Note that (\ref{eq:accref}) can be regarded as a definition of minimal
%acceptances by means of maximal refusals. In this case,
%(\ref{eq:accinitials}) and (\ref{eq:accsubset}) are consequences of this
%definition and the fact that refusals are subset-closed. \fixme{alcc: are you
%sure? (4) does not talk about Acc. Is this important?}
%\fixme{jp: I'm sure and I can prove this. However, we don't need this fact, so I suggest to
%removed it.}
%
Exploiting formulas (\ref{eq:accref}), (\ref{eq:accinitials}), and
(\ref{eq:accsubset}), every node of a normalised transition graph can
alternatively be labelled with their minimal acceptances, and this
information is equivalent to that contained in the maximal refusals. Since
process states $P/s$ are equivalently expressed by states $G(P)/s$ of $P$'s
normalised transition graph, we also write $\minaccs(G(P)/s)$ and
note that (\ref{eq:refsAndR}) and (\ref{eq:accref}) imply
\begin{equation}\label{eq:maxrefsminaccs}
\minaccs(G(P)/s) = \{ \Sigma - R | R\in r(G(P)/s) \}.
\end{equation}
\fixme{alcc: proof in the report perhaps?}

@@

\begin{example}\label{ex:a}
We consider the process $P$ in Example~\ref{example:CSP}; its transition
graph $G(P)$ is shown in Fig.~\ref{fig:tga}. The process state
$P/\varepsilon$ (where $\varepsilon$ denotes the empty trace) is represented
as Node\_0, with $\{ a\}$ as the only minimal acceptance, since $a$ is never
refused and no other events are accepted. Having engaged in $a$, the
transition from Node\_0 leads to Node\_2 representing the process state $P/a
= Q\intchoice R$. The internal choice induces several minimal acceptances
derived from $Q$ and $R$. Since these processes accept their initial events
in external choice, $Q\intchoice R$ induces minimal acceptance sets $\{a,c\}$
and $\{b,c\}$. We note that the event $c$ can never be refused, since it is
contained in each minimal acceptance set.

Having engaged in $c$, the next process state is represented by Node\_1. Due
to normalisation, there is only a single transition satisfying
$t(\text{Node\_2},c) = \text{Node\_1}$. This transition, however, can have
been caused by either $Q$ or $R$ engaging into $c$, so Node\_1 corresponds to
process state $Q/c \intchoice R/c = P \intchoice R$. This is reflected by the
two minimal acceptance sets labelling Node\_1. Similar considerations explain
the other nodes and transitions in Fig.~\ref{fig:tga}.

Note that the node names including their number suffixes are generated by the
FDR tool. The numbering is generated during the normalisation procedure. So,
the node numbers do not reflect the distance from the initial node Node\_0.
\xbox
\end{example}
%
Summarising, refinement relations between finite-state CSP processes $P, Q$ can be be
expressed by means of their normalised transition graphs
\begin{eqnarray*}
G(P) & = & ( N_P, {\ii n}_P, \Sigma, t_P : N_P\times\Sigma \pfun N_P, r_P : N_P \fun \mathbb{P}\mathbb{P}(\Sigma))
\\
G(Q) & = & ( N_Q, {\ii n}_Q, \Sigma, t_Q : N_Q\times\Sigma \pfun N_Q, r_Q : N_Q \fun \mathbb{P}\mathbb{P}(\Sigma))
\end{eqnarray*}
%
as established by results in the following lemma.
%
\begin{lemma}
  \label{lemma:tgtrcref}
  \begin{eqnarray}
  P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
  \label{eq:trcrefa}
  \\
  \label{eq:failconf}
  P \lessdet_F Q & \Leftrightarrow & P \lessdet_T Q \wedge P\ conf\ Q
  \\
  \label{eq:failrefa}
  P\ conf\ Q & \Leftrightarrow & \nonumber
  \forall s\in\trc(G(Q))\cap \trc(G(P)), R_Q\in r_Q(G(Q)/s):  \nonumber
  \\ & & \tabd
  \exists R_P\in r_P(G(P)/s): R_Q\subseteq R_P
  \\
  \label{eq:failrefb}
   & \Leftrightarrow &
    \forall s\in\trc(G(Q))\cap \trc(G(P)), A_Q\in\minaccs(G(Q)/s):  \nonumber
   \\ & & \tabd
  \exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
 \end{eqnarray}
  \xbox
\end{lemma}
%
The result (\ref{eq:trcrefa}) reflects trace refinement in terms of graph
traces; (\ref{eq:failconf}) expresses failures refinement in terms of traces
refinement and $conf$; (\ref{eq:failrefa}) states how $conf$ can be expressed
by means of the maximal refusal functions of the graphs involved; and
(\ref{eq:failrefb}) states the same in terms of the minimal acceptances that
can be derived from the maximal refusal functions by means of
(\ref{eq:maxrefsminaccs}). \fixme{alcc: I think at least the report should
point to proofs.}

% =========================================================================
\subsubsection*{Reachability Under Sets of Traces}
\label{sec:V} Given a finite-state CSP process $P$ and its normalised
transition graph $G(P)$,
%\[
%G(P) = ( N, \ii n, \Sigma, t : N\times\Sigma \pfun N, r : N \fun \mathbb{P}\mathbb{P}(\Sigma)),
%\]
we suppose that $V\subseteq\Sigma^*$ is a prefix-closed set  of sequences of
events. By $t(\ii n,V)$ we denote the set
\[
t(\ii n,V) = \{ n\in N~|~\exists s\in V: s\in\trc(P)\wedge G(P)/s = n \}
\]
of nodes in $N$ that are reachable in $G(P)$ by applying traces of $V$. The
lemma below specifies a construction method for such sets $V$ reaching {\it
every} node of $N$.

@@

For proving our main theorems, it is necessary to consider the \emph{product}
of normalised transition graphs. We need this only for the investigation of
corresponding traces in reference processes and processes for SUTs. So, the
labelling of nodes with maximal refusals or minimal acceptances are
disregarded in the product construction. We consider two normalised
transition graphs
\[
G_i = ( N_i, \ii n_i, \Sigma, t_i : N_i\times\Sigma \pfun N_i, r_i : N_i \fun \mathbb{P}\mathbb{P}(\Sigma)),\qquad i = 1,2,
\]
over the same alphabet $\Sigma$. Their product is defined by
%
\begin{eqnarray}
G_1\times G_2 & = & (N_1\times N_2,(\ii n_1,\ii n_2), t:(N_1\times N_2)\times\Sigma\pfun (N_1\times N_2))
\\
\dom~t & = & \{ ((n_1,n_2),e)\in (N_1\times N_2)\times\Sigma~|   \nonumber
\\ & & \tabc
(n_1,e)\in\dom~t_1\wedge
(n_2,e) \in\dom~t_2    \}
\\
t((n_1,n_2),e) & = & (t_1(n_1,e),t_2(n_2,e))\ \text{for $((n_1,n_2),e)\in\dom~t$}
\end{eqnarray}
%
The following lemma is used in the proof of our main theorem.
%
\begin{lemma}\label{lemma:reachproduc}
If $G_1$ has $p$ states and $G_2$ has $q$ states, then every reachable state
$(n_1,n_2)$ of the product graph $G_1\times G_2$ can be reached by a trace
%%%$s\in\trc(G_1)\cap \trc(G_2)$  we don't need this
of maximal length $(pq-1)$.
\end{lemma}
\begin{proof}
The product graph $G_1\times G_2$ has at most $pq$ states. The empty trace $\varepsilon$
reaches its initial state $(\ii n_1,\ii n_2)$. Applying Lemma~\ref{lemma:extendV}
$(pq-1)$ times with $V=\{\varepsilon \}$ implies that $G_1\times G_2$ reaches
all of its reachable states (there are at most $pq$ of them) under
$V' = V \cup V.\Sigma\cup\dots \cup V.\Sigma^{(pq-1)}$. The maximal length of traces in
$V'$ is $(pq-1)$.
\xbox
\end{proof}
\fixme{Abrupt end to the section. It has more than just preliminary material.
It has some new results.}

@@

\item For all $s\in\trc(P)\cap \trc(Q)$ and $H \in  \minhits(P/s)$, $H$ is
a (not necessariliy minimal) hitting set of $\minaccs(Q/s)$.
\end{enumerate}
\end{lemma}
\begin{proof}
For showing ``$1 \Rightarrow 2$'', assume   $P\ conf\ Q$ and $s\in\trc(P)\cap
\trc(Q)$. Lemma~\ref{lemma:tgtrcref} (\ref{eq:failrefb}), states that
\[
\forall A_Q\in\minaccs(G(Q)/s):
\exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
\]
Therefore, $H \in  \minhits(P/s)$ not only implies $H\cap A_P\neq\varnothing$
for all minimal acceptances $A_P$, but also $H\cap A_Q\neq\varnothing$ for
every minimal acceptance $A_Q$, because $A_P\subseteq A_Q$ for at least one
$A_P$. As a consequence, each $H \in \minhits(P/s)$ is also a hitting set for
$\minaccs(G(Q)/s)$ as required.
